The Psychology of Online Political Hostility -- How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents

### 2024-02-13 starter_folder-main/paper/paper.qmd
bibliography added

####Workspace setup ####
library(tidyverse)
library(janitor)
library(knitr)
library(ggplot2)
library(ggpubr)
library(kableExtra)

@@

Since as early as 2000, there has been a desire for people to engage in political discussions anonymously through social media platforms (Dahlberg, 2001). With the rapid expansion and development of the internet, it has become extremely common for individuals to connect to it using electronic devices. By 2024, the registered user base of the leading social media platform, Instagram, had reached an astounding 2.5 billion (1). This staggering number serves as compelling evidence for the global shift into the internet era. However, along with the globalization of the internet, a series of problems arising from online interactions have become increasingly apparent, with one of the most notable being the toxic atmosphere prevalent in online discussions. Nowadays, online discussions are rife with users launching vicious attacks against each other, and according to a survey conducted in the United States, politics is one of the most contentious topics that easily sparks heated debates (Duggan, 2017). Furthermore, apart from the chaos caused by personal attacks among individual users, online trolling has also become a tool for manipulating public opinion. For instance, researchers have found that during elections, social media users engage in partisan attacks that completely overshadow substantive issues, leading to a wave of partisan confrontation (2). Today, online political hostility has been identified as a " key question for achieving impact on online harassment" (Matias, 2016, 1).

Scholars have begun to analyze the reasons behind people's more hostile behavior in online communication and the psychological factors behind it. Some analysts suggest that when individuals communicate without facing someone directly, but rather in an anonymous or difficult-to-trace environment, even those who are usually friendly may find it challenging to control their emotions, especially on controversial topics (Baek, Wojcieszak, and Delli Carpini, 2012; Cheng et al., 2017; Stein, 2016). The lack of regulators and accountability mechanisms in online discussions seems to be one of the reasons for this hostility. Additionally, the flat structure of social media allows people from different social backgrounds to participate in discussions on the same political issues. Therefore, compared to offline communication, online communication is more likely to result in disagreements over political discourse, and individuals with conflicting views are more likely to encounter each other (Brundidge, 2010). In general, the characteristics of the internet and social media amplify people's emotions and increase the likelihood of political disagreements occurring.

The article "The Psychology of Online Political Hostility: A Comprehensive, Cross-National Test of the Mismatch Hypothesis" analyzes the differences in people's behavior in online and offline political discussions and draws some conclusions. They collected data through online surveys in the United States and Denmark from 2018 to 2021, totaling approximately 4800 responses, and conducted a series of analyses. They found that people perceive differences between online and offline political discussions but do not necessarily believe that online political discussions are more hostile than offline ones. Furthermore, in self-assessments, people believe that they exhibit similar levels of aggression in online and offline environments and do not perceive offline political discussions to be more peaceful than online ones (Bor Alexander and Michael Bang Petersen, 2021). We noticed that their survey questionnaire, in addition to investigating online and offline discussions on political topics, also asked respondents to assess their own personalities, such as "I consider myself a calm person" or "I am an aggressive person." Therefore, we decided to replicate this article and conduct secondary research based on the data they collected.

@@

[^1]: Rstudio [@citeR] was used for producing the code and this paper. A series of R packages were used: [@gg2]. [@knitr], [@kable], [@janet], and [@tidy].

@@

## Source
The paper used for replication is from the "American Political Science Review," which analyzed and compared the level of aggressiveness in people's online and offline political discussions, using surveys as a means of data collection (Bor Alexander and Michael Bang Petersen, 2021). Our replication aims to address a new question stemming from the original paper: whether individuals with more aggressive personalities exhibit greater differences in behavior between online and offline political discussions.

@@

This paper will replicate the survey data originally collected for the study by Bor Alexander and Michael Bang Petersen (2021). They selected the United States and Denmark as the source of the original data, considering them to be two countries with stark differences in many aspects, thus likely to produce more credible original data (Bor Alexander and Michael Bang Petersen, 2021). The United States was characterized as a high-polarization, high-conflict, low-trust, and low-participation country, while Denmark was described as a low-polarization, low-conflict, high-trust, and high-participation country (Nelson and Shavitt, 2002). Surveys were disseminated across multiple public platforms to collect feedback from users of different platforms, aiming to obtain the most authentic responses, as some social platforms may censor highly aggressive political discourse.

@@

In (@fig-tab-two), we observe that the p-values for online and offline hostility levels, whether in the overall dataset or in the individual datasets from the United States and Denmark, far exceed 0.05. This suggests that there is no significant difference in hostility levels between online and offline political discussions. This finding is consistent with the conclusion drawn in the original paper (Bor Alexander and Michael Bang Petersen, 2021). However, in the t-tests comparing online/offline hostility levels between the United States and Denmark, we note that the p-values are less than 0.05. This indicates a significant difference in the level of political discussion hostility between the United States and Denmark, both in online and offline settings.

@@

Firstly, as mentioned earlier, the data used in this study comes from the original data of Bor Alexander and Michael Bang Petersen's research. Although they collected over 4800 survey results from the United States and Denmark, the data from Denmark amounted to only about one thousand, while the data from the United States overwhelmingly dominated with around 3800 responses. Despite the data from the United States being used extensively, the imbalance in sample sizes between the two countries may lead to errors in the overall data results. This is because the United States was characterized as a high-polarization, high-conflict, low-trust, and low-participation country, while Denmark was described as a low-polarization, low-conflict, high-trust, and high-participation country (Nelson and Shavitt, 2002), and researchers believed that these opposite characteristics could make the results representative of a wider range of applications. In fact, we also verified this point in the results,  in online and offline political discussions, the hostility level of the American sample was significantly higher than that of the Danish sample. Therefore, the unequal sample sizes of the United States and Denmark may bias the research results towards the political discussion environment in the United States.

Secondly, the data collection method, which is questionnaire,  may also affect the accuracy of the survey results. Firstly, as a form of survey that allows respondents to fill in voluntarily, the questionnaire can only collect subjective answers from respondents, without objective evaluation. For example, in the question "Are you an even-tempered person," the respondent may actually have a quick temper, but subjectively believes that they are a calm person, and the questionnaire can only yield "even-tempered" as a result. Secondly, although the survey was posted on various websites, not limited to a single social media platform, data was not collected both in online and offline environment, which could introduce sampling bias. Moreover, when respondents see the survey information online and voluntarily participate in the survey, individuals who are more relevant to the survey information and those with specific personalities may be more inclined to participate in the survey, rather than closing the webpage. (Imagine someone who afraid of inconvenience seeing a survey, they are more likely to ignore it than participate in filling it out.) Therefore, when online surveys are sent to people we don't know, and when only some people choose to take part spontaneously, the survey results might not be very reliable (Andrade C. 2020).

@@

>>>>

####Workspace setup ####
library(tidyverse)
library(janitor)
library(knitr)
library(ggplot2)
library(kableExtra)

@@

Since as early as 2000, there has been a desire for people to engage in political discussions anonymously through social media platforms [@dahl]. With the rapid expansion and development of the internet, it has become extremely common for individuals to connect to it using electronic devices. By 2024, the registered user base of the leading social media platform, Instagram, had reached an astounding 2.5 billion [@insta]. This staggering number serves as compelling evidence for the global shift into the internet era. However, along with the globalization of the internet, a series of problems arising from online interactions have become increasingly apparent, with one of the most notable being the toxic atmosphere prevalent in online discussions. Nowadays, online discussions are rife with users launching vicious attacks against each other, and according to a survey conducted in the United States, politics is one of the most contentious topics that easily sparks heated debates [@duggan]. Furthermore, apart from the chaos caused by personal attacks among individual users, online trolling has also become a tool for manipulating public opinion. For instance, researchers have found that during elections, social media users engage in partisan attacks that completely overshadow substantive issues, leading to a wave of partisan confrontation [@rosse]. Today, online political hostility has been identified as a " key question for achieving impact on online harassment" [@matias].

Scholars have begun to analyze the reasons behind people's more hostile behavior in online communication and the psychological factors behind it. Some analysts suggest that when individuals communicate without facing someone directly, but rather in an anonymous or difficult-to-trace environment, even those who are usually friendly may find it challenging to control their emotions, especially on controversial topics [@baek]. The lack of regulators and accountability mechanisms in online discussions seems to be one of the reasons for this hostility. Additionally, the flat structure of social media allows people from different social backgrounds to participate in discussions on the same political issues. Therefore, compared to offline communication, online communication is more likely to result in disagreements over political discourse, and individuals with conflicting views are more likely to encounter each other [@brun]. In general, the characteristics of the internet and social media amplify people's emotions and increase the likelihood of political disagreements occurring.

The article "The Psychology of Online Political Hostility: A Comprehensive, Cross-National Test of the Mismatch Hypothesis" analyzes the differences in people's behavior in online and offline political discussions and draws some conclusions. They collected data through online surveys in the United States and Denmark from 2018 to 2021, totaling approximately 4800 responses, and conducted a series of analyses. They found that people perceive differences between online and offline political discussions but do not necessarily believe that online political discussions are more hostile than offline ones. Furthermore, in self-assessments, people believe that they exhibit similar levels of aggression in online and offline environments and do not perceive offline political discussions to be more peaceful than online ones [@oripaper]. We noticed that their survey questionnaire, in addition to investigating online and offline discussions on political topics, also asked respondents to assess their own personalities, such as "I consider myself a calm person" or "I am an aggressive person." Therefore, we decided to replicate this article and conduct secondary research based on the data they collected.

@@

[^1]: Rstudio [@citeR] was used for producing the code and this paper. A series of R packages were used: [@gg2], [@knitr], [@kable], [@janet], and [@tidy].

@@

## Source
The paper used for replication is from the "American Political Science Review," which analyzed and compared the level of aggressiveness in people's online and offline political discussions, using surveys as a means of data collection [@oripaper]. Our replication aims to address a new question stemming from the original paper: whether individuals with more aggressive personalities exhibit greater differences in behavior between online and offline political discussions.

@@

This paper will replicate the survey data originally collected for the study by Bor Alexander and Michael Bang Petersen. They selected the United States and Denmark as the source of the original data, considering them to be two countries with stark differences in many aspects, thus likely to produce more credible original data [@oripaper]. The United States was characterized as a high-polarization, high-conflict, low-trust, and low-participation country, while Denmark was described as a low-polarization, low-conflict, high-trust, and high-participation country [@nels]. Surveys were disseminated across multiple public platforms to collect feedback from users of different platforms, aiming to obtain the most authentic responses, as some social platforms may censor highly aggressive political discourse.

@@

In (@fig-tab-two), we observe that the p-values for online and offline hostility levels, whether in the overall dataset or in the individual datasets from the United States and Denmark, far exceed 0.05. This suggests that there is no significant difference in hostility levels between online and offline political discussions. This finding is consistent with the conclusion drawn in the original paper [@oripaper]. However, in the t-tests comparing online/offline hostility levels between the United States and Denmark, we note that the p-values are less than 0.05. This indicates a significant difference in the level of political discussion hostility between the United States and Denmark, both in online and offline settings.

@@

Firstly, as mentioned earlier, the data used in this study comes from the original data of Bor Alexander and Michael Bang Petersen's research. Although they collected over 4800 survey results from the United States and Denmark, the data from Denmark amounted to only about one thousand, while the data from the United States overwhelmingly dominated with around 3800 responses. Despite the data from the United States being used extensively, the imbalance in sample sizes between the two countries may lead to errors in the overall data results. This is because the United States was characterized as a high-polarization, high-conflict, low-trust, and low-participation country, while Denmark was described as a low-polarization, low-conflict, high-trust, and high-participation country [@nels], and researchers believed that these opposite characteristics could make the results representative of a wider range of applications. In fact, we also verified this point in the results,  in online and offline political discussions, the hostility level of the American sample was significantly higher than that of the Danish sample. Therefore, the unequal sample sizes of the United States and Denmark may bias the research results towards the political discussion environment in the United States.

Secondly, the data collection method, which is questionnaire,  may also affect the accuracy of the survey results. Firstly, as a form of survey that allows respondents to fill in voluntarily, the questionnaire can only collect subjective answers from respondents, without objective evaluation. For example, in the question "Are you an even-tempered person," the respondent may actually have a quick temper, but subjectively believes that they are a calm person, and the questionnaire can only yield "even-tempered" as a result. Although there's one question asking for comments from the others -- "My friends say that I’m somewhat argumentative.", this is not enough to reflect other people's objective views. Secondly, although the survey was posted on various websites, not limited to a single social media platform, data was not collected both in online and offline environment, which could introduce sampling bias. Moreover, when respondents see the survey information online and voluntarily participate in the survey, individuals who are more relevant to the survey information and those with specific personalities may be more inclined to participate in the survey, rather than closing the webpage. (Imagine someone who afraid of inconvenience seeing a survey, they are more likely to ignore it than participate in filling it out.) Therefore, when online surveys are sent to people we don't know, and when only some people choose to take part spontaneously, the survey results might not be very reliable [@andr].

@@

In future research, we can make the following improvements in data collection to increase the reliability of the results: Firstly, in addition to the United States and Denmark, we can involve other countries with different political characteristics in the survey and  maintain a similar sample size for each country.
Secondly, apart from distributing surveys online, we can also distribute the same questionnaire offline to collect data from both online and offline environments simultaneously.
Thirdly, we can try to include more questions that collect objective data and compare others' evaluations of the respondents with the respondents' self-evaluations. If there is a significant difference, we may consider excluding the data.

Furthermore, in this study, we found that the level of aggression does not affect the hostility exhibited by individuals in online and offline political discussions. Therefore, we will explore other factors that may contribute to the difference in hostility between online and offline discussions. Additionally, since we obtained the same results as the original paper,  that is there is no significant difference in hostility between online and offline political discussions, we can also investigate the interesting question: if there is no difference in hostility between online and offline discussions, why do people generally perceive online discussions as more hostile? This will be an important direction for our future research.
